---
title: "Tidy Tuesday: Ramen ratings"
author: "Jason Gullifer"
date: "June 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(glmnet)
library(Matrix)

theme_set(theme_minimal(base_size = 12))
```

```{r}
ramen_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv")
```

# Inspect the data
```{r}
str(ramen_ratings)

ramen_ratings %>% 
  count(brand, sort=T) 

ramen_ratings %>% 
  count(variety, sort=T)

ramen_ratings %>% 
  count(style, sort=T)

ramen_ratings %>% 
  count(country, sort=T)

```


# Data cleaning
```{r}
ramen_ratings <- ramen_ratings %>% 
  mutate(brand = fct_lump(brand, n=10),
         style = fct_lump(style, n=3),
         country = fct_lump(country, 10),
         style = replace_na(style, "Other")) %>%
  filter(!is.na(review_number))
```

# Inspect lumped factors
```{r}
ramen_ratings %>% 
  count(brand, sort=T) 

ramen_ratings %>% 
  count(variety, sort=T)

ramen_ratings %>% 
  count(style, sort=T)

ramen_ratings %>% 
  count(country, sort=T)

ramen_ratings %>% 
  group_by(country, brand) %>% 
  summarise(n())
```

# Density plot of star ratings
```{r}
ramen_ratings %>% 
  ggplot(aes(x=stars))+geom_density()
```

# Box plots of star ratings
```{r}
ramen_ratings %>% 
  group_by(brand) %>% 
  mutate(mstars = median(stars, na.rm=T)) %>% 
  ungroup() %>% 
  mutate(brand = fct_reorder(brand, mstars)) %>% 
  ggplot(aes(y=stars, x=brand)) + geom_boxplot() + coord_flip()

ramen_ratings %>% 
  group_by(style) %>% 
  mutate(mstars = median(stars, na.rm=T)) %>% 
  ungroup() %>% 
  mutate(style = fct_reorder(style, mstars)) %>% 
  ggplot(aes(y=stars, x=style)) + geom_boxplot() + coord_flip()

ramen_ratings %>% 
  group_by(country) %>% 
  mutate(mstars = median(stars, na.rm=T)) %>% 
  ungroup() %>% 
  mutate(country = fct_reorder(country, mstars)) %>% 
  ggplot(aes(y=stars, x=country)) + geom_boxplot() + coord_flip()
```


# Average ratings by brand, style, and country
```{r}

ramen_ratings %>% 
  group_by(brand) %>% 
  summarise(meanStars = mean(stars, na.rm=T)) %>% 
  mutate(brand = fct_reorder(brand, meanStars)) %>% 
  ggplot(aes(y=meanStars, x=brand)) + geom_col() + xlab("Ramen brand") + ylab("Mean star rating")

ramen_ratings %>% 
  group_by(style) %>% 
  summarise(meanStars = mean(stars, na.rm=T)) %>% 
  mutate(style = fct_reorder(style, meanStars)) %>% 
  ggplot(aes(y=meanStars, x=style)) + geom_col() + geom_col() + xlab("Ramen style") + ylab("Mean star rating")

ramen_ratings %>% 
  group_by(country) %>% 
  summarise(meanStars = mean(stars, na.rm=T)) %>% 
  mutate(country = fct_reorder(country, meanStars)) %>% 
  ggplot(aes(y=meanStars, x=country)) + geom_col() + geom_col() + xlab("Country of origin") + ylab("Mean star rating")
```


# Average ratings by brand + style and by country + style
```{r}
rr_summ <- ramen_ratings %>% 
  group_by(country, brand) %>% 
  summarise(meanStars = mean(stars, na.rm=T), sdStars = sd(stars, na.rm=T), N=n()) %>% 
  ungroup() %>% 
  group_by(country) %>%
  mutate(meanCStars = mean(meanStars)) %>% 
  ungroup() %>% 
  group_by(brand) %>%
  mutate(meanBStars = mean(meanStars)) %>% 
  ungroup() %>%
  mutate(country = fct_reorder(country, meanCStars),
         brand = fct_reorder(brand, meanBStars))

rr_summ %>%
  ggplot(aes(y=meanStars, colour=brand, x=country, ymin=meanStars - sdStars, ymax = meanStars+sdStars)) + 
  geom_pointrange(position=position_dodge(width=.9)) + coord_flip() + scale_colour_brewer(palette = "BrBG") + guides(colour = guide_legend(reverse = TRUE, title="Ramen style")) + ylab("Mean rating (in stars)") + xlab("Ramen brand")



rr_summ <- ramen_ratings %>% 
  group_by(country, style) %>% 
  summarise(meanStars = mean(stars, na.rm=T), sdStars = sd(stars, na.rm=T), N=n(), sem=sdStars / sqrt(N)) %>% 
  ungroup() %>% 
  group_by(country) %>%
  mutate(meanCStars = mean(meanStars)) %>% 
  ungroup() %>% 
  group_by(style) %>%
  mutate(meanSStars = mean(meanStars)) %>% 
  ungroup() %>%
  mutate(country = fct_reorder(country, meanCStars),
         style = fct_reorder(style, meanSStars))

rr_summ %>%
  ggplot(aes(y=meanStars, colour=style, x=country, ymin=meanStars - sem, ymax = meanStars+sem)) + 
  geom_pointrange(position=position_dodge(width=.9)) + coord_flip() + scale_colour_brewer(palette = "BrBG") +guides(colour = guide_legend(reverse = TRUE, title = "Ramen style")) + ylab("Mean rating (in stars)")+ xlab("Ramen country of origin")

```

# Lexical analysis of ramen varieties
```{r}
rr_u <- ramen_ratings %>% 
  unnest_tokens(word, variety) %>% 
  anti_join(get_stopwords()) %>% 
  mutate(word=fct_lump(word, n = 30))

rr_u %>% 
  count(word, sort=T)

rr_u %>% 
  mutate(meanStars = mean(stars, na.rm=T),
         diffStars = stars - meanStars) %>% 
  group_by(word) %>% 
  summarise(meanDiff = mean(diffStars, na.rm=T),
            sdDiff   = sd(diffStars, na.rm=T),
            N=n(),
            sem = sdDiff/sqrt(N)) %>% 
  mutate(word=fct_reorder(word, meanDiff),
         pos_neg = ifelse(meanDiff < 0, "Below average", "Above average"),
         pos_neg = factor(pos_neg, levels=c("Below average", "Above average"))) %>% 
  ggplot(aes(x=word, y=meanDiff, ymin=meanDiff-sem, ymax=meanDiff+sem, fill=pos_neg)) + 
  geom_col() + geom_errorbar(width=.2) +
  coord_flip() + guides(fill = guide_legend(reverse = TRUE, title = "Rating")) +
  ylab("Mean difference in star rating") + xlab("Word in variety description") + ggtitle("Ramen ratings by words in description") 

```


# Lasso regression on word, brand, country, style

## Create model matrices
```{r}
rr <- na.omit(ramen_ratings)

rr$review_number <- 1:nrow(rr)

rr_u <- rr %>% 
  unnest_tokens(word, variety) %>% 
  anti_join(get_stopwords())

mm <- rr_u %>%
  mutate(word=paste0("Word_",word)) %>% 
  cast_sparse(review_number, word)

mmc <- rr %>%
  mutate(country=paste0("Country_",country)) %>% 
  cast_sparse(review_number, country)

mmb <- rr %>% 
  mutate(brand=paste0("Brand_",brand)) %>% 
  cast_sparse(review_number, brand)
 
mms <- rr %>% 
  mutate(style=paste0("Style_",style)) %>% 
  cast_sparse(review_number, style) 


mm <- cbind(mm, mmc, mmb, mms)
```

## Run cross-validated glmnet model and show lambda plot
```{r}

cv_glmnet_model = cv.glmnet(x=mm,y = rr$stars)
plot(cv_glmnet_model)
```

## Extract model fit
```{r}
fit <- cv_glmnet_model$glmnet.fit %>%
  tidy() %>% 
  filter(term != "(Intercept)",
         lambda == cv_glmnet_model$lambda.min) %>% 
  separate(term, into=c("factor","level"), sep="_")
```

## Effects for words
```{r}
lexicon <- fit %>% 
  filter(factor=="Word") %>%
  select(word = level, coefficient = estimate)

lexicon %>%
  arrange(coefficient) %>%
  group_by(direction = ifelse(coefficient < 0, "Negative", "Positive")) %>%
  top_n(20, abs(coefficient)) %>%
  ungroup() %>%
  mutate(word = fct_reorder(word, coefficient)) %>%
  ggplot(aes(word, coefficient, fill = direction)) +
  geom_col() +
  coord_flip() +
  labs(x = "",
       y = "Estimated effect of the word on the rating",
       title = "What words are predictive of a ramen star rating?")
```

## Effects for country of origin
```{r}

country <- fit %>% 
  filter(factor=="Country") %>%
  select(country = level, coefficient = estimate)

country %>%
  arrange(coefficient) %>%
  group_by(direction = ifelse(coefficient < 0, "Negative", "Positive")) %>%
  ungroup() %>%
  mutate(country = fct_reorder(country, coefficient)) %>%
  ggplot(aes(country, coefficient, fill = direction)) +
  geom_col() +
  coord_flip() +
  labs(x = "",
       y = "Estimated effect of the Country on the rating",
       title = "What countries are predictive of a ramen star rating?")
```

## Effect for brand
```{r}
brand <- fit %>% 
  filter(factor=="Brand") %>%
  select(brand = level, coefficient = estimate)

brand %>%
  arrange(coefficient) %>%
  group_by(direction = ifelse(coefficient < 0, "Negative", "Positive")) %>%
  ungroup() %>%
  mutate(brand = fct_reorder(brand, coefficient)) %>%
  ggplot(aes(brand, coefficient, fill = direction)) +
  geom_col() +
  coord_flip() +
  labs(x = "",
       y = "Estimated effect of the brand on the rating",
       title = "What brands are predictive of a ramen star rating?")
```

## Effects for style
```{r}

style <- fit %>% 
  filter(factor=="Style") %>%
  select(style = level, coefficient = estimate)

style %>%
  arrange(coefficient) %>%
  group_by(direction = ifelse(coefficient < 0, "Negative", "Positive")) %>%
  ungroup() %>%
  mutate(style = fct_reorder(style, coefficient)) %>%
  ggplot(aes(style, coefficient, fill = direction)) +
  geom_col() +
  coord_flip() +
  labs(x = "",
       y = "Estimated effect of the style on the rating",
       title = "What styles are predictive of a ramen star rating?")
```